\sys: Automated Data-Parallel Shell Processing

### 2020-04-07 pldi/draft.tex
Notes on pldi draft

@@

>>>>

\subsection{Implementation Nuggets}

\TODO{Problem: Cat (and other commands that have multiple inputs) is
  not eager. Illustration: Show a parallel pipeline having a cat that
  gathers input somewhere (and a sort merge maybe). The way pipes
  work, this graph will essentially evaluate almost completely
  sequentially. Maybe go through the steps that cat asks for the first
  line of its first input until ithe first input is done and then goes
  to the second. This leads to processor under-utilization. Solution:
  We add eager nodes that eagerly consume all their input (even if
  their output does not ask for it). Eager nodes are themselves part
  of the dataflow graph (and model) and essentially perform an
  identity function. This makes all processors as utilized as possible
  and for CPU heavy tasks it leads to speedup. For IO heavy (and CPU
  light) tasks it has some overhead. We evaluate eager in section X
  (We should also say something about a CPU light task).}

\TODO{(This problem is a nice followup for the one above) Problem:
  Dataflow graph termination. Illustration: Show the example of head
  deadlock and explain that this is inherent behaviour in the shell.
  (Solution: emptying pipelines or terminating processes) In order for
  things to terminate gracefully, dish wraps all commands in order to
  always consume all of their input by sending it down to
  /dev/null. Warning: This means that all commands in the pipeline
  must terminate if all of their output is consumed. We evaluate the
  overhead of emptying all outputs in section X.}

\TODO{Problem: Pipeline width shrinks after parallel pure
  commands. Solution: Split node that resplits its input to multiple
  files in sequence (to preserve the model semantics). We should
  probably evaluate that too.}

@@

\TODO{Notes on Unix50. We got the Unix50 solutions as is and we ran
  them. These are the numbers. By changing fmt -w1 to tr (or by adding
  it appropriately to the DSL) and by changing some occurences of awk
  to ..., the speedup in these cases goes to...}

\TODO{Remember to mention that deathstar has 128 threads but 64
  cores. So it is reasonable for the speedup to not go further in cpu
  heavy pipelines.}
